Patient-Specific Neural Field Modeling from Mirco-Electrode Data

### 2010-07-19 ltx/data_paper/DataPaper.tex
added note to paper about the connectivity kernel decomp

A property of the Gaussian basis function decomposition it that the Gaussianality of the disturbance term is maintained. The decomposition disturbance term is defined as

@@

>>>>

A property of the basis function decomposition it the preservation of the Gaussianality of the disturbance term. The decomposition disturbance term is defined as

@@

\dean{I will do the connectivity kernel decomposition bit after the correlation analysis, because we can use it to say something about heterogeneity and isotropy.}
